# Course Info {#info}

(ref:email) [paternnj@plu.edu](mailto:paternnj@plu.edu)

**Instructor:** Nick Paterno

**Email:** (ref:email)

### Office Hours
Sign up [here](https://calendar.google.com/calendar/u/0/selfsched?sstoken=UUEtUG1vWXBzQWVnfGRlZmF1bHR8MDkxZTNlNTE2MzdjYTI4ZTY2MmFkNmRlZjI0OTNlNDI)

```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
library(tidyverse)
Day <- c("Monday", "Tuesday", "Thursday")
Hours <- c("8:00 am - 2:30 pm", rep("1:00 pm - 3:00 pm",2))
df <- data.frame(Day, Hours)
knitr::kable(df) 
```
*Campus:* Morken 261 

*Virtual:* via Zoom or Google Meet. 

### Class Schedule
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
library(tidyverse)
Day <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
Activity <- c("New video lessons posted", "Student hours", "Student hours", "Code along/live coding sessions", "Workshops")
df <- data.frame(Day, Activity)
knitr::kable(df) 
```

### Class Materials

**Textbook:** [OpenIntro Statistics, 4th Ed](https://leanpub.com/openintro-statistics)

#### Technology:

* Access to a word processing program. 
* [R](https://cran.r-project.org/) and [RStudio](https://rstudio.com/) (These are free and we will get them setup during our first lab day)
* A graphing calculator, preferably a TI-83 or TI-84. A Casio FX-9750GII will also work (useful but *optional*).

## Graded Items and Grading Guidelines
<center> *This section is a work in progress and will likely change* </center>

### Weights of Grades:
Category  | Weight
------------- | -------------
Homework  | 20%
Quizzes  | 20%
Labs | 20%
Paper | 15%
Final|  25%
Total   | 100%

#### Homework:
All homework assignments will be online. For these assignments, you will have 3 attempts per question. After the third attempt you will be shown the answer. You can reattempt each question as many times as you'd like! Homework must be completed by 11:59 pm. You will not be able to complete the quiz until you have finished the week's homework assignments with a 50% or better! Your lowest 2 assignments will be dropped.

#### Quizzes:
Each module will have weekly quizzes. The quiz will be locked until you meet the prerequisites. Your lowest 2 quizzes will be dropped. If you miss a quiz it counts as one of your drop scores.

#### Labs:
We will have a total of seven computer lab days. Those dates are listed below (see Important Dates) and in the *Welcome email*. Your lowest two labs will be dropped.

#### Paper:
Each student will be required to write a paper about statistics in the media. Details will be given out in the second week of class via the Class Communications guidelines. The paper is due no later than the Last Day of Instruction (see Important Dates below). If there is a week where you don't have much work in your other classes or our class didn't take you long then you may want to knock out the paper early in the semester.

#### Final:
The final project will be partly in R and partly on WAMAP. It will be due no later than Friday, May 28.

### Important Dates
Date  | Event
------------- | -------------
2/25/2021 | Lab #1
3/4/2021 | Lab #2
3/18/2021 | Lab #3
3/25/2021 | Lab #4
4/2/2021  | No Class: Good Friday
4/8/2021 | Lab #5
4/29/2021 | Lab #6
5/6/2021 | Lab #7
5/21/2021 | Last Day of Instruction
5/24/2021-5/28/2021 | Finals Week
